This page and the next page should be removed

### 2021-04-05 analysis/manuscript.Rmd
update docker

# Create an export folder for results
dir.create("analysis/export", showWarnings = FALSE)

@@

# Read behavioral data for Experiment 1
list.files("data/exp1/RT", pattern = ".txt", full.names = TRUE) %>% map(read_behav) -> behav_exp1

@@

# Preprocess the EEG for Experiment 1 in Python
map2(
  .x = list.files("data/exp1/EEG", pattern = ".vhdr", full.names = TRUE),
  .y = behav_exp1,
  ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
) %>%
  # Concatenate epochs of all participants
  py$mne$epochs$concatenate_epochs() -> epochs_exp1

# Backup epochs to the export folder
epochs_exp1$save("analysis/export/exp1-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp1) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
  write_tsv("analysis/export/exp1-data.tsv") -> data_exp1

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
  saveRDS("analysis/export/exp1-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
  write_tsv("analysis/export/exp1-objects.tsv")

# Get standard EasyCap electrode positions and project to 2D space
py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
  read_tsv(col_types = cols()) %>%
  rename(electrode = Site) %>%
  inner_join(tibble(electrode = epochs_exp1$ch_names), ., by = "electrode") %>%
  mutate(
    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
  ) %>%
  write_tsv("analysis/export/montage.tsv")

@@

An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @serre2007]. In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition. For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this "barrier of meaning" [@mitchell2020]. Drawing inspiration from cognitive psychology and human neuroscientific data may help to make these models more biologically plausible and, at the same time, more data efficient.

>>>>

# Create an export folder for results
dir.create("export", showWarnings = FALSE)

@@

# Read behavioral data from two batches of participants
paste0("data/rt/exp", 1:2) %>%
  map(list.files, pattern = ".txt", full.names = TRUE) %>%
  map(map, read_behav) -> behav

# Avoid duplicate participant labels across the two batches
behav[[2]] %<>% map(mutate, participant = paste0(participant, "_2"))

# Merge into a single list
behav %<>% flatten()

@@

# Preprocess the EEG for Experiment 1 in Python
paste0("data/eeg/exp", 1:2) %>%
  list.files(pattern = ".vhdr", full.names = TRUE) %>%
  map2(
    .y = behav,
    ~ do.call(py$preproc, c(list(vhdr_fname = .x, metadata = .y), preproc_params))
  ) %>%
  # Concatenate epochs of all participants
  py$mne$epochs$concatenate_epochs() -> epochs

# Backup epochs to the export folder
epochs$save("export/aha-epo.fif")

# Compute mean ERP amplitudes and bind to the behavioral data
pmap_dfc(comps, py$compute_erps, epochs = epochs_exp1) %>%
  set_names(comps$name) %>%
  bind_cols(as_tibble(epochs_exp1$metadata), .) %T>%
  write_tsv("export/exp1-data.tsv") -> data_exp1

# Compute grand averages per part and condition
py$compute_evokeds(epochs = epochs_exp1, grand = TRUE, data_only = TRUE) %>%
  saveRDS("export/exp1-gaverages.RDS")

# Backup number of stimuli assigned to each condition for all participants
map(behav_exp1, function(x) table(x$condition) / 3) %>%
  bind_rows() %>%
  mutate(Participant = unique(data_exp1$participant), .before = 1) %>%
  write_tsv("export/exp1-objects.tsv")

# Get standard EasyCap electrode positions and project to 2D space
py$mne$channels$`_standard_montage_utils`$MONTAGE_PATH %>%
  list.files(pattern = "easycap-M1.txt", full.names = TRUE) %>%
  read_tsv(col_types = cols()) %>%
  rename(electrode = Site) %>%
  inner_join(tibble(electrode = epochs_exp1$ch_names), ., by = "electrode") %>%
  mutate(
    x = eegUtils:::deg2rad(Theta) * cos(eegUtils:::deg2rad(Phi)),
    y = eegUtils:::deg2rad(Theta) * sin(eegUtils:::deg2rad(Phi)),
  ) %>%
  write_tsv("export/montage.tsv")

@@

An interactive view of object vision with an abundance of top-down feedback also challenges the predominantly feed-forward models in computer vision [e.g., @marr1982; @lindsay2020]. In fact, the lack of a semantic knowledge base that dynamically interacts with the processing of lower-level visual features may be one key reason why even state-of-the-art deep-learning algorithms need orders of magnitude more training examples to achieve human-level performance in object recognition. For these network models, single-trial learning of previously unfamiliar objects, as was observed on the behavioral and on the neurophysiological level in the present study, seems to be out of reach until they overcome this "barrier of meaning" [@mitchell2020]. Drawing inspiration from cognitive psychology and human neuroscientific data may help to make these models more biologically plausible and, at the same time, more data efficient.
